\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\setlength{\footskip}{4.5pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.25in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \scshape\centering
}{}{0em}{}[\color{black}\titlerule]


\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item
    {#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingExtra}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-2em}
}

\newcommand{\resumeSubheadingEducation}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

{\LARGE \scshape Henrique Vicente de Oliveira Pinto}\\
\href{mailto:henriquevicente@gmail.com}{henriquevicente@gmail.com}\\
\vspace{1em}
Website: \href{https://henvic.dev/}{https://henvic.dev}\\
GitHub: \href{https://github.com/henvic}{https://github.com/henvic}\\
LinkedIn: \href{https://linkedin.com/in/henvic}{https://linkedin.com/in/henvic}

%-----------EXPERIENCE-----------
\vspace{1em}
\textbf{Summary:} Software engineer with 15 years of professional experience working in the software development industry, with an \href{https://henvic.dev/portfolio/}{portfolio of several products and projects}.
Seasoned {\href{https://henvic.dev/opensource/}{open-source software contributor}} with experience \href{https://henvic.dev/talks/}{speaking} at diverse events in Europe, South, and North America.

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Engineer}{Nov 2023 -- Present}
      {Self-employed contractor}{Remote}
      \resumeItemListStart
        \resumeItem{Contractor with over 15 years of software engineering experience and 9 years with the Go programming language.}
        \resumeItem{Work with technologies such as Go, PostgreSQL, Elasticsearch/OpenSearch, Kubernetes, authentication/authorization with authorization with OAuth, authentication with OpenID, monitoring distributed systems with OpenTelemetry, Grafana, Terraform, Google Cloud, and Amazon Web Services.}
        \resumeItem{Implementation of new solutions adopting Go to match existing implementations to spec using reverse engineering.}
      \resumeItemListEnd
      \resumeSubheading
      {Senior Software Engineer}{Aug 2022 -- Apr 2023}
      {Form3}{Remote}
      \resumeItemListStart
        \resumeItem{Worked in the Core Data team of the London-based Cloud-native Payment Processing Platform Form3 on internal services that handle payment and payment returns.}
        \resumeItem{Experience with Go, gRPC, NATS, PostgreSQL, Kubernetes, Terraform, and multi-cloud environments.}
      \resumeItemListEnd
      \resumeSubheading
      {Senior Software Engineer}{Feb 2021 -- Jul 2022}
      {Stitch, PVH Corp.}{The Netherlands}
      \resumeItemListStart
        \resumeItem{Led a comprehensive project to enhance developer experience, ensure reliability, improve efficiency, and reduce operational costs by planning and implementing a robust automated testing infrastructure with fast integration tests (2s on average for the entire test suite) and replacing a non-relational database with PostgreSQL and Elasticsearch/OpenSearch.}
        \resumeItem{As part of the preceding goal, we yield a remarkable impact: a lasting expense reduction of over 90\% of our recurring database cloud computing and licensing expenses and enhanced software development efficiency throughout multiple teams.}
        \resumeItem{Worked on multiple web services with API development with Go, Kubernetes, Terraform, and other technologies.}
        \resumeItem{Worked on data migration of media assets from renowned fashion brands, including internal clients such as Tommy Hilfiger and Calvin Klein and external ones such as Havaianas and Scotch \& Soda.}
        \resumeItem{Experience with Go, gRPC, GraphQL, Kubernetes, Terraform, and Amazon Web Services.}
      \resumeItemListEnd
      \newpage
    \resumeSubheading
      {Senior Software Engineer}{Jun 2019 -- Jan 2021}
      {HousingAnywhere}{The Netherlands}
      \resumeItemListStart
        \resumeItem{On the platform team, worked public-facing RESTful APIs, internal services, and integration with affiliate partners.}
        \resumeItem{Worked on the payment system and payouts infrastructure with Stripe.}
        \resumeItem{Experience with Go, gRPC, Google Cloud Platform, Kubernetes, and microservices.}
    \resumeItemListEnd
    \resumeSubheadingExtra
      {Senior Software Engineer}{Jan 2018 -- May 2019}
    \resumeSubheading
      {Software Engineer}{Mar 2014 -- Dec 2017}
      {Liferay, Inc.}{Brazil}
      \resumeItemListStart
        \resumeItem{As a key member of WeDeploy / Liferay DXP in its early days, led the development of its CLI tool, which was the primary client developers utilized to access and use the platform.}
        \resumeItem{Developed sophisticated solutions using Go and JavaScript for front and backend libraries and applications, such as reverse-engineering the socket.io protocol to use it for emulating an SSH connection.}
        \resumeItem{Worked on multiple front-end open-source programs, libraries, and frameworks maintained by the company for internal and external use.}
        \resumeItem{Experience with deploying desktop applications to end-users on multiple platforms (macOS, Linux, and Windows).}
        \resumeItem{Experience with function and integration tests for a diverse range of applications (web-based and desktop-based CLI tools for internal and external developers).}
        \resumeItem{Led the development of a CLI tool for managing GitHub very similar to today’s GitHub CLI tool many years before an official tool had been released.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

\parbox[t]{\dimexpr\linewidth-0.95em}{
  \hspace{0.95em}\parbox[t]{\dimexpr\linewidth-0.95em}{
    {\textbf{Important:} For an extensive look at greenfield projects I've initiated independently or collaborated on during previous employment, as well as insights into my significant career, please visit my \href{https://henvic.dev/portfolio}{portfolio page} on my website.}
  }
}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Bachelor of Science in Computer Science}{October 2013 -- December 2017}
      {Universidade Federal de Pernambuco}{}
      \resumeSubheading
      {EMC Academic Associate}{2017}
      {Cloud Infrastructure and Services}{}
  \resumeSubHeadingListEnd

%-----------Highlights-----------
\section{Hightlights}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item{
     \textbf{Interests}{: Open-source software, Software Engineering, Photography, Nature, Skiing, Drones, Homelab, Airplanes, Industrial Design, Electric Vehicles (EV), piano, music.} \\
      \textbf{Keywords}{: gRPC, Protobuf, HTTP(S), REST API, Go, JavaScript, Java, Unix scripting, cloud computing, Kubernetes, CI, CD, SQL, PostgreSQL, OpenSearch, Elasticsearch, Terraform, Grafana, Security, dev tools, DNS, networking, Linux, macOS, FreeBSD, VMware ESXi, golang.}
    }
 \end{itemize}
 
\end{document}
