\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\centering
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}



\begin{center}
    {\LARGE \scshape Henrique Vicente de Oliveira Pinto} \\ \vspace{2pt}
    \begin{multicols}{2}
    \begin{flushleft}
    \href{https://henvic.dev/}{https://henvic.dev}\\
    \href{https://linkedin.com/in/henvic}{https://linkedin.com/in/henvic}\\
    \end{flushleft}
    
    \begin{flushright}
    \href{mailto:henriquevicente@gmail.com}{henriquevicente@gmail.com}\\
    \href{tel:+31-6-29-11-54-82}{+31-6-29-11-54-82}
    \end{flushright}
    \end{multicols}
\end{center}


%-----------EDUCATION-----------
\vspace{-2pt}
\section{Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Universidade Federal de Pernambuco}{October 2013 -- December 2017}
      {Bachelor of Science in Computer Science}{Recife, Brazil}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Senior Software Engineer}{February 2021 -- Present}
      {HATCH, PVH Corp.}{Amsterdam, Netherlands}

    \resumeSubheading
      {Senior Software Engineer}{June 2019 -- January 2021}
      {HousingAnywhere}{Rotterdam, Netherlands}
      \resumeItemListStart
        \resumeItem{Worked on the Platform team on internal and public-facing APIs, services, and integration with affiliate partners.}
        \resumeItem{Worked on the Payments team on the backend of the payments and payouts infrastructure.}
        \resumeItem{Experience with Go, Google Cloud Platform, Kubernetes, and microservices.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Senior Software Engineer}{January 2018 -- May 2019}
      {Liferay Cloud}{Remote}
    \resumeSubheading
      {Software Engineer}{March 2014 -- December 2017}
      {Liferay, Inc.}{Recife, Brazil \& Remote}
      \resumeItemListStart
        \resumeItem{Designed, implemented, and maintained projects such as the CLI tool of WeDeploy and Liferay Cloud DXP.}
        \resumeItem{Experience developing projects with Go and JavaScript (frontend and backend).}
        \resumeItem{Reverse engineered the socket.io protocol to create a remote access protocol emulating SSH.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Co-Founder, Software Engineer}{c. 2013 -- 2015}
      {Vehikel}{}
      \resumeItemListStart
        \resumeItem{Created this online marketplace for vehicles, inspired by Craigslist and eBay using PHP, ElasticSearch, MySQL, etc.}
        \resumeItem{Implemented a real-time search engine with faceted filters, and pages with maps, edit-in-place, and photo carousel.}
        \resumeItem{Implemented a web crawler for extracting data from industry sources on the web using CasperJS and PhantomJS.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Software Engineer}{October 2012 -- July 2013}
      {MGR Tecnologia – Cahier corporate social network}{Recife, Brazil}
      \resumeItemListStart
        \resumeItem{Introduced static analysis tools to improve code quality for the PHP backend.}
        \resumeItem{Fixed slow pages loading time by profiling bottlenecks, and refactoring PHP code and MySQL/PostgreSQL queries.}
        \resumeItem{Lead the implementation of a chat system with Node.js.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Software Engineer}{March 2011 -- December 2011}
      {Ogilvy \& Mather}{Recife, Brazil}
      \resumeItemListStart
        \resumeItem{Contract work for several Fortune 500 clients projects using a PHP and MySQL stack.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Founder, Software Engineer}{c. 2009 -- 2011}
      {Plifk}{}
      \resumeItemListStart
        \resumeItem{File-sharing web service. UX with a progressive enhancement mindset. API with OAuth support.}
        \resumeItem{Experience with cloud computing (AWS), Linux, PHP, JavaScript, Memcached, and MySQL.}
    \resumeItemListEnd
    
    
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills, Language Skills, and Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Operating Systems}{: Linux, macOS, VMware ESXi (beginner).} \\
     \textbf{Programming Languages}{: Go (proficient), JavaScript, PHP, Unix scripting, Java, TCL.} \\
     \textbf{Software development}{:  Cloud computing, Security, Linux, macOS, CLI tools, developer tooling, Kubernetes, CI, SQL.} \\
     \textbf{Languages}{: Portuguese (native), English (fluent), Dutch (beginner).} \\
     \textbf{Interests}{: Open-source software, Photography, Nature, Travel, Drones, Industrial design, Homelab, Airplanes.}
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications \& Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Dell EMC Academic Associate}{: \href{https://www.certmetrics.com/DellEmc/public/verification.aspx?code=Z043ZNDTJMB11QS1}{Cloud Infrastructure and Services. Certificate issued on June 12, 2017}} \\
     \textbf{Zend Certified Engineer}{: \href{https://www.zend-zce.com/en/yellow-pages/ZEND013948}{PHP 5. Certificate issued on May 13, 2010}} \\
     \textbf{New York Film Academy}{: 4-week filmmaking workshop during January, 2009} \\
     \textbf{Brazilian Physics Olympiad}{: \href{https://sec.sbfisica.org.br/olimpiadas/obf2004/resultadofinal_2serie.htm}{Honors, 2004}}
     }}
 \end{itemize}

\end{document}
